I would like to express my special thanks of gratitude to my professors (Prof. Honiden Shinichi, Prof. Tei Kenji, Prof. Sakamoto Kazunori, and Prof. Chiba Shigeru) who gave me the opportunity to explore freely on any projects, which allows this research to be conducted. I would like to thank Prof. Honiden for continuing his supervising on me even after his retirement from the University of Tokyo. I would like to thank Prof. Tei for helping me finalize this project and advising me on my research skills. I would like to thank Prof. Sakamoto for designing the proposed methods with me and offering me his extensive knowledge on machine learning. I would like to thank Prof. Chiba for being my official advisor at the University of Tokyo after the retirement of Prof. Honiden.

Secondly, I would also like to express my sincere gratitude to all the participants and especially to those (Shen Xin, Kang Yi) who have helped invite their friends to join this research. I would like to express my gratitude to Juku Momo, a growing tutoring center located in Saitama, for allowing me to conduct the data collection on the students there. Without the help from all my friends and my friends' friends, this research would not be possible. All the participants' efforts are especially important to this research and to me personally. I would like to once again thank all of them to be a part of this research. Thank you.

Finally, I would like to thank the University of Tokyo for having me conduct research here and providing many resources for research purpose. It is a great honor to be a member of the Graduate School of Information Science and Technology at the University of Tokyo. 

